### 2024-10-11 manuscript.tex
Update README.md [ci skip]
This build is based on
https://github.com/pivlab/annual_review_of_biomedical_data_science/commit/f41444a381bda8bb691bbc6dce8a0ecf4e2888da.

This commit was created by the following CI build and job:
https://github.com/pivlab/annual_review_of_biomedical_data_science/commit/f41444a381bda8bb691bbc6dce8a0ecf4e2888da/checks
https://github.com/pivlab/annual_review_of_biomedical_data_science/actions/runs/11286109742

This manuscript
(\href{https://pivlab.github.io/annual_review_of_biomedical_data_science/v/c71300a3cad92282ed84fc78b2c02dcdd08a9852/}{permalink})
was automatically generated
from \href{https://github.com/pivlab/annual_review_of_biomedical_data_science/tree/c71300a3cad92282ed84fc78b2c02dcdd08a9852}{pivlab/annual\_review\_of\_biomedical\_data\_science@c71300a}
on October 11, 2024.

>>>>

This manuscript
(\href{https://pivlab.github.io/annual_review_of_biomedical_data_science/v/f41444a381bda8bb691bbc6dce8a0ecf4e2888da/}{permalink})
was automatically generated
from \href{https://github.com/pivlab/annual_review_of_biomedical_data_science/tree/f41444a381bda8bb691bbc6dce8a0ecf4e2888da}{pivlab/annual\_review\_of\_biomedical\_data\_science@f41444a}
on October 11, 2024.
